Verifying Demonstrations

### 2020-04-15 paper/adversary-model.tex

The adversary maliciously controls \(W\) (the strongest role a
participant can take on).
The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
like everyone else (\ie a malicious protester~\(P\)).
The adversary only learns the protocol data, \ie what is sent over the 
channel --- no auxiliary data such as who is on the other side of the channel obtained
  as side information, \eg by face recognition or inference from address
  to identity.

>>>>

The goal of the adversary is to link a protester's real identity~\(P\) to a 
protest identifier~\(\cid\).
The adversary maliciously controls \(W\).
The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
like everyone else (\eg a malicious protester~\(P\)).
The adversary only learns the protocol data, \ie what is sent over the channel 
--- no auxiliary data such as who is on the other side of the channel obtained
  as side information, \eg by face recognition or inference from address
  to identity.

### 2020-04-15 paper/distance-bounding.tex
Fixes authors in a row

\subsection{\Acl*{DB} protocols}%
\label{distance-bounding}

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on his distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account. 
At the end of a \Ac{DB} protocol, the verifier should be able to determine if the prover is legitimate \emph{and} in his vicinity.
In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.

There are four adversaries for \ac{DB} protocols established in the literature, 
each of which tries to commit a type of fraud.
These can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates using a, 
    possibly honest, prover who is far away from the verifier.
    (Also known as relaying attack or man-in-the-middle attack.)
  \item \Acf{DBTF}: a legitimate, but malicious, prover helps an accomplice, 
    who is close to the verifier, to authenticate.
    \Ac{DBTF} resistance is a very strong property; it implies that if the 
    accomplice succeeds (with non-negligible probability) he will learn the 
    prover's secret key\footnote{%
      This means that even things like functional encryption will not help.
    }.
  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 
    uses an unsuspecting honest prover close to the verifier to pass as being 
    close.
    (This is different from \ac{DBMF} in that the honest prover actually tries 
    to authenticate to the verifier, but the malicious prover hijacks the 
    channel at some point(s) during the protocol.)
\end{itemize}

The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
In this context it does not make sense to protect against the verifier as he 
can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
We will work in the latter setting; with a \emph{malicious verifier} who will 
potentially try to \emph{impersonate the prover} after successful verification.

\subsection{\Acl*{DB} security definitions}%
\label{DB-definitions}

There are two lines of attempts at formalizing the above properties: one by 
\citet{DB-BMV} and another by \citet{DB-DFKO}.
We will use the framework of \citeauthor{DB-DFKO} with extensions by 
\textcite{FormalTerroristFraud} and \textcite{TREAD} (definitions in 
\cref{DB-definitions}).

As summarized in by \textcite{TREAD}, there are three types of sessions for an 
adversary:
\begin{description}
  \item[Prover--verifier] The adversary observes an honest execution.
  \item[Prover--adversary] The adversary runs the protocol as a verifier with 
    an honest prover.
  \item[Adversary--verifier] The adversary runs the protocol as a, potentially 
    malicious, prover with an honest verifier.
\end{description}
Each session is associated with a unique identifier \(\sid\).
Each adversary is defined in terms of
computational resources, time~\(t\);
number of prover--verifier sessions observed, \(\qobs\);
number of prover--adversary sessions initiated, \(\qp\), and
number of adversary--verifier sessions initiated, \(\qv\).

The DFKO framework~\cite{DB-DFKO} uses an abstract clock~\(\marker\colon \NN\to 
  \NN\) which is strictly increasing and orders the adversary's actions.
We let
\(\Xscript{\sid}{i, \dotsc, j}\)
denote the sequence of messages
\((m_i, \dotsc, m_j)\)
exchanged during the session \(\sid\).

A session consists of three phases: a setup phase, a time-critical phase and a 
verification phase.
Both setup and verification can be run slowly, but the time-critical phase must 
be run as fast as possible.

\paragraph*{\Acl*{DBMF}}

We will now define the conditions for \ac{DBMF} and \ac{DBMF} resistance.
A tainted session is a session in which the adversary lost because the verifier 
detected the attempt at cheating, \eg the timing is too long because the 
adversary is out of range.
The following definition captures a pure relay and a verifier is assumed to 
detect such a relay.

\begin{definition}[Tainted session, \acs*{DBMF}~\cite{DB-DFKO}]%
  \label{TaintedMF}
  A time-critical round
  \(\Xscript{\sid}{k, k+1} = (m_k, \dotsc, m_{k+1})\)
  of an adversary--verifier session~\(\sid\), where \(m_k\) is sent by the 
  verifier, is \emph{tainted} by the round
  \(\Xscript{\sid'}{k', k'+1} = (m_{k'}, m_{k'+1})\)
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    (m_k, m_{k+1}) &= (m_{k'}, m_{k'+1}) \\
    \marker[\sid, k] &< \marker[\sid', k'] \\
    \marker[\sid, k+1] &> \marker[\sid', k'+1].
  \end{align*}
\end{definition}

We will now define what it means for a protocol to be \ac{DBMF} resistant.

\begin{definition}[\acs*{DBMF} resistance~\cite{TREAD}]%
  \label{MFresistance}
  For \iac{DB} authentication scheme \(\DB\), a \((t, \qobs, \qp, \qv)\)-MF 
  adversary \(\adv\) \emph{wins} against \(\DB\) if the verifier accepts 
  \(\adv\) in in one of the \(\qv\) adversary--verifier sessions \(\sid\), 
  which does not have any critical phase tainted by a prover--adversary session 
  \(\sid'\).
  The protocol \(\DB\) is \Ac{DBMF} resistant if the probability 
  \(\Adv_{\DB}^{\text{MF}}(\adv)\) that \(\adv\) wins is negligible in the 
  security parameter.
\end{definition}

\paragraph*{\Acl*{DBTF}}

\Acl{DBTF} is similar to \ac{DBMF}, the difference is that during \ac{DBTF} the 
prover cooperates with the adversary to make the verifier accept.

\begin{definition}[Tainted session, \acs*{DBTF} 
  (strSimTF)~\cite{FormalTerroristFraud}]\label{TaintedTF}
  A time-critical round
  \[\Xscript{\sid}{k, \dotsc, k+2l-1} = (m_k, \dotsc, m_{k+2l-1}),\] for 
  \(l\geq 1\), of an adversary--verifier session~\(\sid\), where \(m_k\) is 
  sent by the verifier, is \emph{tainted} by the round
  \[\Xscript{\sid'}{k, \dotsc, k+2l-1} = (m'_{k}, \dotsc, m'_{k+2l-1})\]
  of a prover--adversary session~\(\sid'\) if
  \begin{align*}
    \marker[\sid, k+2i] &< \marker[\sid', k+2i] \\
    \marker[\sid, k+2i+1] &> \marker[\sid', k+2i+1].
  \end{align*}
\end{definition}

Then we have the following definition of security.

\begin{definition}[SimTF security~\cite{DB-DFKO}]%
  \label{TFresistance}
  Let \(\DB\) be an authentication scheme for parameters \((t_{\max}, T_{\max}, 
    E_{\max}, N_c)\).
  Let \(\adv\) be a \((t, \qv, q_{\F})\)-SimTF adversary, \(\S\) an algorithm 
  with runtime \(t_{\S}\) and \(\F\) an algorithm with runtime \(t_{\F}\).
  Let \[
    \Adv_{\DB}^{\text{TF}}(\adv, \S, \F) = p_{\adv} - p_{\S},
  \] where \(p_{\adv}\) is the probability that the verifier~\(V\) accepts in 
  one of the \(\qv\) adversary--verifier sessions~\(\sid\) such that at 
  \(T_{\max}\) time-critical phases of \(\sid\) are tainted and \(p_{\S}\) is 
  the probability that, given the state of \(\adv\), \(\S\) authenticates to 
  the verifier~\(V\) in one of \(\qv\) subsequent executions.
\end{definition}

\paragraph*{\Acl*{DBDH} and \acl*{DBDF}}

The final property is \ac{DBDH} and \ac{DBDF}.
The following definitions for \ac{DBDH} also captures \ac{DBDF} 
attacks~\cite{TREAD}.
We first define what the adversary can and cannot do by defining a tainted 
session for \ac{DBDH}.

The intuition is that an adversary (malicious, far-away prover) must commit to 
an action: either respond with an own message, which is determined before 
seeing the challenge, or to prompt a nearby prover to respond (with a message 
chosen by the adversary).
Technically, this adversary can do more than \iac{DBDH} adversary normally can.
\Textcite{TREAD} captured this by two dummy sessions \(\sid_{\Commit}\) and 
\(\sid_{\Prompt}\).
The adverary commits to his action by \enquote{sending} \((\sid, k+1, 
m'_{k+1})\) in dummy session \(\sid_{\Commit}\) before receiving the challenge 
in message \(k\) in session \(\sid\) (making message \(k+1\) in \(\sid\) his 
response to the challenge).
If \(m'_{k+1} = \Prompt\), then he must also \enquote{send} a message in dummy 
session \(\sid_{\Prompt}\), which is the message the nearby prover will send.

\begin{definition}[Tainted session, \acs*{DBDH}~\cite{TREAD}]%
  \label{TaintedDH}
  A time-critical round \(\Xscript{\sid}{k, k+1} = (m_k, m_{k+1})\), for some 
  \(k\geq 1\) and \(m_k\) send by the verifier, of an adversary--verifier 
  session \(\sid\) is \emph{tainted} if one of the following conditions holds.
  \begin{itemize}
    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
      m_{k+1}')\) for \(m_{k+1}' \neq \Prompt\) and \(\marker[\sid, k] > 
      \marker[\sid_{\Commit}, j]\) satisfies \(m_{k+1}' \neq m_{k+1}\) (or no 
      such \(j\) exists).

    \item The maximal \(j\) with \(\Xscript{\sid_{\Commit}}{j} = (\sid, k+1, 
      m_{k+1}')\) for \(m_{k+1}' = \Prompt\) satisfies \(m_{k+1} \neq 
      m_{k+1}^{\Prompt}\), in which \(m_{k+1}^{\Prompt}\) denotes the message 
      \(m_{k+1}\) in \(\sid_{\Prompt}\).
  \end{itemize}
\end{definition}

To win, the adversary must convince a verifier that he is close when he 
actually is not and without tainting any of the sessions.

\begin{definition}[\acs*{DBDH} resistance~\cite{TREAD}]%
  \label{DHresistance}
  For \iac{DB} authentication scheme~\(\DB\) with \ac{DB} threshold 
  \(t_{\max}\), a \((t, \qp, \qv, \qobs)\)-\ac{DBDH} adversary \(\adv\) wins 
  against \(\DB\) if the verifier accepts \(\adv\) in one of the \(\qv\) 
  adversary--verifier sessions without any critical round being tainted.
  Thus, \ac{DBDH} resistance is defined as the probability 
  \(\Adv_{\DB}^{\text{DH}}(\adv)\) that \(\adv\) wins the game.
\end{definition}

>>>>

\subsection{Distance-bounding protocols}%
\label{distance-bounding}

\Ac{DB} protocols were first suggested by \citet{DistanceBounding} to prevent relay attacks in contactless communications in which the adversary forwards a communication between a prover and a possibly far-away verifier to authenticate. 
These attacks cannot be prevented by cryptographic means as they are independent of the semantics of the messages exchanged.
As a consequence, mechanisms ensuring the physical proximity between a verifier and a prover should be used instead.
\Ac{DB} protocols precisely enable the verifier to estimate an upper bound on their distance to the prover by measuring the time-of-flight of short challenge-response messages (or rounds) exchanged during time-critical phases. 
Time critical phases are complemented by slow phases during which the time is not taking into account. 
At the end of a \Ac{DB} protocol, the verifier should be able to
determine if the prover is legitimate \emph{and} in their vicinity.
In this sense, \Ac{DB} protocols combine the classical properties of authentication protocols with the possibility of verifying the physical proximity.

There are four adversaries for \ac{DB} protocols established in the literature, 
each of which tries to commit a type of fraud.
These can be summarized as follows:
\begin{itemize}
  \item \Acf{DBDF}: a legitimate but malicious prover wants to fool the verifier on the distance between them.
  \item \Acf{DBMF}: the adversary illegitimately authenticates using a, 
    possibly honest, prover who is far away from the verifier.
    (Also known as relaying attack or man-in-the-middle attack.)
  \item \Acf{DBTF}: a legitimate, but malicious, prover helps an accomplice, 
    who is close to the verifier, to authenticate.
    \Ac{DBTF} resistance is a very strong property; it implies that if the 
    verifier accepts the accomplice with non-negligible probability the 
    accomplice can compute the prover's secret key\footnote{%
      This means that even things like functional encryption will not
      help the adversary.
    }.
  \item \Acf{DBDH}: similar to \ac{DBDF}, the malicious prover is far away but 
    uses an unsuspecting honest prover close to the verifier to pass as being 
    close.
    (This is different from \ac{DBMF} in that the honest prover actually tries 
    to authenticate to the verifier, but the malicious prover hijacks the 
    channel at some point(s) during the protocol.)
\end{itemize}
% There are two lines of attempts at formalizing the above properties: one by \citet{DB-BMV} and another by \citet{DB-DFKO}.

% The majority of the existing \ac{DB} protocols are symmetric and thus require an honest verifier.
% Indeed, in this context it does not make sense to protect against the
% verifier as they can easily impersonate the prover as they have knowledge of their secret key.
% There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will potentially try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to 
their actions, thus we also require strong privacy.
In fact, as the construction in \cref{Protocol} shows, we require \iac{DB} 
\ac{ZKPK}, or simply \ac{PPK}, for discrete logarithms.
For this paper, we assume the existence of such a protocol.
There exists \ac{PPK} schemes, \eg~\cite{ProProx}, just no published scheme for 
discrete logarithms yet\footnote{%
  The authors have such a protocol under submission in another venue.
}.

### 2020-04-15 paper/intro.tex

\paragraph*{Contributions}

We make three contributions.
First, we provide a version of the Schnorr protocol that is \ac{DBMF}, 
\ac{DBTF}, \ac{DBDH} and \ac{DBDF} resistant in the DFKO 
model~\cite{DB-DFKO,FormalTerroristFraud,TREAD}.
This version is based on the assumption that we can transmit all bits at once, 
not bit-by-bit as normally required for \ac{DB}.
This assumption is reasonable by the results of \textcite{UWBPR}.

Second, for the assumption about sending all bits at once to hold, 
\textcite{UWBPR} requires that two devices shared a symmetric key~\(k\).
Our second contribution is \iac{PKI} and \ac{AKE} scheme for any device in 
the \ac{PKI} to convince a verifier that this is the case.
This replaces everyone having the same static key~\(k\) with everyone having a 
unique key which is signed by \iac{CA} of the \ac{PKI}, which allows for 
revocation.
The solution relies on our first contribution.

Our last contribution is another version of the protocol, one which uses 
bit-by-bit transmissions as traditionally done with \ac{DB} protocols.
We achieve all properties except \ac{DBTF} resistance.

The first (and second) contribution enables us to do distance-bounding 
privacy-preserving attribute-based credentials based on discrete logarithms, 
\eg \cite{Camenisch-phdthesis} and \cite{CLsignatures}.
To our knowledge, no other distance-bounding protocol achieves this.
The third contribution (bit-by-bit version) also enables us to do the same, 
just without \ac{DBTF} resistance.

\paragraph*{Outline}

The paper is organized as follows.
\Cref{Preliminaries} introduces the preliminaries of \ac{ZKPK} and \ac{DB}.
\Cref{DB-Schnorr} introduces the first version, where we assume that we can 
send all bits at the same time.
\Cref{DB-Schnorr-PKI} introduces the \ac{PKI} and \ac{AKE} to use the first 
version of the protocol in practice.
\Cref{DB-Schnorr-nbit} describes the bit-by-bit version of the protocol.
\Cref{formal-verification} describes our effort to formally verify the protocol 
using Tamarin.
Finally, we conclude with discussion and conclusions in 
\cref{Discussion,Conclusion}.

>>>>

%\emph{Context.}

While our proposal is meant for crowd counting in general and to be applicable to any kind of event, we represent an event with a political protest against an oppressive regime throughout the paper. We choose this instantiation of an event because it is the most challenging in terms of requirements for privacy and verifiability (transparency).

Historically, there are many examples of protests in which the count estimated by police and that of the organizers differ significantly, sometimes by hundreds of thousands.
Even without foul play, the difference is quite natural as both parties have different objectives and metrics.
More precisely, the organizers want to count everyone who participated while the police want to estimate the count at the peak of participation, due to crowd control~\cite{2016DemonstrationsInSeoul}.
Among the numerous recent examples in which it is difficult to establish the actual number of participants, there are the demonstrations against the president in South Korea~\cite{2016DemonstrationsInSeoul}, Trump's inauguration~\cite{HowWillWeKnowTrumpInauguralCrowdSize}, the 2017 Women's March in the US~\cite{2017WomensMarchesInUS}, the demonstrations against the change of constitution in Venezuela~\cite{AlJazeeraOnVenezuela2017} or for the independence of Catalonia~\cite{CataloniaDemonstrations}.

Consider the following scenario.
Alice is an activist that organizes a protest in some location(s) against the current government, represented by Grace.
Alice wants to estimate the number of participants to prove a certain support for her cause against Grace in a way that is both demonstrably accurate and does not increase the participants' risk of retribution against them from Grace's regime. 
To realize this objective, a reliable yet privacy-preserving crowd-counting mechanism is needed, which to the best of our knowledge is a problem that has not yet been entirely solved.

Existing methods for crowd-counting vary significantly in terms of approaches.
% (we will review them in detail in \cref{current-crowd-counting}).
Most of them, however, lack precision (\ie they have large error margins) and can only give an estimate for a particular snapshot in time, not the cumulative participation count --- at least not without counting some persons multiple times.  In addition, they lack verifiability in the sense that one has to trust the third party responsible for implementing the counting method.

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) has an incentive to decrease it.
%In this case, we are left with two options: either we trust Alice or Grace (or another third party) or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice 
and Grace from cheating by providing verifiable participation counts that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. While one cannot
prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest, we do not want the digital traces of our protocol to increase any risk for the participants.

%we have to ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity. % and that any witnessing is also unlinkable.
%\seb{in the sentence above I am not sure that the word unlinkable will be 
%  necessary clear}

%\paragraph*{Contributions}

%Our first contribution is \CROCUS, a privacy-preserving scheme that provides a 
%way to securely estimate crowd counts in protests\footnote{%
%  If location is ignored, it can be reduced to privacy-preserving yet 
%  verifiable petitions.
%}.
%
%Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
%Our adaptation fulfills all the requirements for modern \ac{DB} protocols, 
%including \ac{DBDH} (which was an attack against the original protocol of 
%Brands and Chaum) and \ac{DBTF}.
%More importantly, it is public-key, handles malicious impersonating verifiers.
%Since it is based on the Schnorr protocol, it provides a distance-bounded 
%\ac{PK} for discrete logarithms.
%That allows us to replace the plain Schnorr protocol in \acp{ZKPK} with our 
%distance-bounding version and thus make general privacy-preserving, 
%attribute-based credential systems distance bounding.

% The paper is organized as follows.
% First, we describe our system model and summarize the desired properties for crowd counting (\cref{system-model}). Next, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \CROCUS (\cref{current-crowd-counting}). 
% We then formalize the notion of protest and the desired verifiability and privacy properties (\cref{definitions}), and we give the relevant background on the building blocks of our solution (\cref{building-blocks}).

The paper is organized as follows.
In \Cref{system-model}, we describe our system model and summarize the desired 
properties for crowd counting, followed by a discussion of current 
crowd-counting methods in \cref{current-crowd-counting}. In \Cref{definitions}, 
we formalize the notion of protest and the desired verifiability and privacy 
properties, and in \cref{building-blocks}, we give the relevant background on 
the building blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
We present \CROCUS, a privacy-preserving crowd counting 
%estimation 
protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
We compare it to related work in \cref{related-work}.
Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.

### 2020-04-15 paper/performance.tex

\section{Performance}%
\label{PerformanceAnalysis}
\sonja{include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}

\subsection{Smartphones and smartcards}
Performance considerations are crucial during the protests due to the nature of the devices used to run \CROCUS, which are resource-constrained in terms of energy, storage and computational power, and are operating on limited network capacity. 
Recent technological progress has enabled the deployment of advanced cryptographic primitives on smartcards and smartphones that could be used to implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices are now fast enough to efficiently implement Privacy Enhancing Technologies (PETs), with a Samsung Galaxy S i9000 being able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to process complex protocols such as Idemix or U-Prove (taking between \SI{4}{\second} and \SI{8}{\second} to process them). 
While the limited processing power of many embarked systems has been a challenge, Idemix has been successfully implemented to prove the possession of credentials on Java Cards by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released in 2014, aimed to achieve an implementation ``suitable for real life transactions''~\cite{IRMA} while maintaining security and privacy for its users.

With respect to its implementation, \CROCUS is actually very similar to Anon-Pass~\cite{AnonPass}, an anonymous subscription system in which a long-term credential can be used to derive a single login for any authentication window (\ie epoch) such that logins are unlinkable across different epochs. 
In particular, the setup and registration phases are almost identical. 
The evaluation conducted by the authors was using as server a Dell Optiplex 780s, which has a quad-core 2.66 GHz Intel Core 2 CPU, 8 GB of RAM and uses Ubuntu Linux 12.04 while the client was also simulated on a quad-core 2.66 GHz Intel Core 2 CPU but with only 4 GB of RAM.
The elliptic pairing group used in Anon-Pass is a Type A symmetric pairing group with a 160-bit group order and 512-bit base field while the ECDSA signature uses a 160-bit key.
This is typically the type of pairing that could also be used with \CROCUS.
Not counting the setup that is performed once by the CA, the time reported for the registration on the server (\ie CA) side is 19.8 milliseconds while it is 23.4 milliseconds on the client side.
With respect to joining and participation phases, with the exception of the distance-bounding they are actually quite similar to the login protocol of Anon-Pass in which the time required to create a message for a protester would be around 13.5 milliseconds while the time needed for the witness would be only 7.9 milliseconds.

\subsection{Distance-bounding anonymous credentials}
The distance-bounding chips~\cite{3dB-access} currently available on the market 
can already enable proofs of proximity for any range of up to 
  200 meters.
One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
More precisely, they have proposed three different implementations of the Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic implementation running a the application layer to an advanced one running in RFID-emulation mode. 
The results obtained already show that a relay attack can be detected if the adversary introduces a delay of more than 1.5 ms when performing such an attack (most of the existing attacks introduce delays of at least tens of milliseconds).

@@

\subsection{Ledger (blockchain) efficiency}
As an example, consider a protest with 1\,000\,000 participants.
If we use trusted witnesses, each participant only needs to acquire one proof share from a trusted witness.
Thus, there will be 1\,000\,000 proof shares submitted to the blockchain in total.
If we consider OmniLedger~\cite{OmniLedger}, which can do approximately 1500 transactions per second, it takes at least 11 minutes to process all the proof shares.

If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
While this already takes longer than counting votes in national elections, the threshold is still very low. 
% Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
% If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
% In addition to the ledger computation, we need to consider the creation of the proof shares. \sonja{added the previous sentence to explain why anonpass shows up here. Shouldn't that be in the performance section? }
% %Seb: I agree maybe we should move it to the previous subsection
% According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
% This yields \(
%   \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
%   \SI{48}{\second}.
% \) of processing. 
For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
Considering that online forums can facilitate mass coordination, the threshold approach with only untrusted witnesses seems not only inefficient but also potentially ineffective for verifiability.

>>>>

\section{Performance}%
\label{PerformanceAnalysis}

\sonja{include evaluation environment, parameters, results, disclaimer about parts that cannot yet be implemented and evaluated because the hardware doesn't exist yet for DB on phones}

Performance considerations are crucial during the protests due to the nature of 
the devices used to run \CROCUS, which are resource-constrained in terms of 
energy, storage and computational power, and are operating on limited network 
capacity.

\subsection{Smartphones and smartcards}

Recent technological progress has enabled the deployment of advanced 
cryptographic primitives on smartcards and smartphones that could be used to 
implement our solution.
For instance, benchmarks~\cite{Benchmarking} have shown that Android devices 
are now fast enough to efficiently implement \acp{PET}, with a Samsung Galaxy S 
i9000 (back in 2014) able to execute Idemix in \SI{153}{\milli\second}. 
However, those benchmarks also demonstrate that smartcards remain slow to 
process complex protocols such as Idemix or U-Prove (taking between 
\SI{4}{\second} and \SI{8}{\second} to process them). While the limited 
processing power of many embarked systems has been a challenge, Idemix has been 
successfully implemented to prove the possession of credentials on Java Cards 
by Bichsel and co-authors in 2009~\cite{Bichsel} and the IRMA project, released 
in 2014, aimed to achieve an implementation ``suitable for real life 
transactions''~\cite{IRMA} while maintaining security and privacy for its 
users.

With respect to its implementation, \CROCUS is very similar to the 
implementation of Anon-Pass~\cite{AnonPass}, an anonymous subscription system 
in which a long-term credential can be used to derive a single login for any 
authentication window (\ie epoch) such that logins are unlinkable across 
different epochs.
In particular, the setup and registration phases are almost identical.
The evaluation conducted by \textcite{AnonPass} used as server a Dell Optiplex 
780s, which has a quad-core 2.66 GHz Intel Core 2 CPU, 8 GB of RAM and uses 
Ubuntu Linux 12.04 while the client was also simulated on a quad-core 2.66 GHz 
Intel Core 2 CPU but with only 4 GB of RAM\@.
The elliptic pairing group used in Anon-Pass is a Type A symmetric pairing group with a 160-bit group order and 512-bit base field while the ECDSA signature uses a 160-bit key.
This is typically the type of pairing that could also be used with \CROCUS\@.
Not counting the setup that is performed once by the \ac{CA}, the time reported 
for the registration on the server (\ie \ac{CA}) side is 
\SI{19.8}{\milli\second} while it is \SI{23.4}{\milli\second} on the client 
side.
With respect to joining and participation phases, with the exception of the 
distance-bounding they are actually quite similar to the login protocol of 
Anon-Pass in which the time required to create a message for a protester would 
be around \SI{13.5}{\milli\second} while the time needed for the witness would 
be only \SI{7.9}{\milli\second}.

%\subsection{Distance bounding}
%
%The distance-bounding chips~\cite{3db-access} currently available on the market 
%can already enable proofs of proximity for any range of up to 
%  200 meters.
%One of the objectives is to be able to integrate them in phones or smartcards in the near future, and even phones with off-the-shelf hardware running in RFID-emulation mode have shown promising results.
%For instance in~\cite{DBonSmartphones}, the authors have demonstrated that it is already possible to implement distance-bounding protocols as a standard Android application on existing smartphones. 
%More precisely, they have proposed three different implementations of the 
%Swiss-Knife protocol using 32 challenge-response rounds ranging from a basic 
%implementation running at the application layer to an advanced one running in 
%RFID-emulation mode. The results obtained already show that a relay attack can 
%be detected if the adversary introduces a delay of more than 1.5 ms when 
%performing such an attack (most of the existing attacks introduce delays of at 
%least tens of milliseconds).

@@

\subsection{Witness processing}

As above, assume we have one trusted witness.
A smartphone ran Idemix in \SI{153}{\milli\second} back in 2014.
3DB-access~\cite{3db-access} says their distance-bounding part takes less than 
\SI{1}{\milli\second} and can do more than \SI{120}{\metre} (line of sight, 
maximum \SI{200}{\metre}).
Then a witness fixed in one position can cover \SI{45216}{\square\metre} 
(\SI{120}{\metre} radius), which fits 137018~protesters according to 
\textcite{2016DemonstrationsInSeoul}.
It would take this witness \SI{5.8}{\hour} to witness all of them.
Thus, to witness 1\,000\,000 protesters, it would take \SI{8}{\hour} for 5.3 
witnesses.

\subsection{Ledger (blockchain) efficiency}

For the example of 1\,000\,000 participants, with trusted witnesses, each 
participant only needs to acquire one proof share from a trusted witness.
Thus, there will be 1\,000\,000 proof shares submitted to the blockchain in total.
If we consider OmniLedger~\cite{OmniLedger}, which can do approximately 1500 transactions per second, it takes at least 11 minutes to process all the proof shares.

%If we do not use trusted witnesses, but instead a threshold \(\theta = 1000\), then it will take at least 7 days before all transactions are committed to the blockchain. 
%While this already takes longer than counting votes in national elections, the threshold is still very low. 
%% Assume that every person has 5000 contacts in their contact book~\cite{DifficultyOfPrivateContactDiscovery}.
%% If collusion were limited to participants that know each other, it could be reasonable to set the threshold of at least 6000 witnesses. 
%% In addition to the ledger computation, we need to consider the creation of the proof shares. \sonja{added the previous sentence to explain why anonpass shows up here. Shouldn't that be in the performance section? }
%% %Seb: I agree maybe we should move it to the previous subsection
%% According to the Anon-Pass performance measures~\cite{AnonPass} each witness signature would require \SI{8}{\milli\second} per core on a quad-core Intel \SI{2.66}{\giga\hertz} Core 2 processors.
%% This yields \(
%%   \SI{8}{\milli\second}\times 6000 = \SI{48000}{\milli\second} = 
%%   \SI{48}{\second}.
%% \) of processing. 
%For large groups organizing online to collectively pretend to participate at a physical protest, the threshold would have to be much higher. 
%Considering that online forums can facilitate mass coordination, the threshold approach with only untrusted witnesses seems not only inefficient but also potentially ineffective for verifiability.
